\documentclass[]{deedy-resume-openfont}

% \hypersetup{%
%   colorlinks=true,% hyperlinks will be black
%   urlcolor=blue
% }

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Rahul}{Nath}{ Website/Blog:\urlstyle{same} \underline{\href{http://therahulnath.com}{\color{blue} http://therahulnath.com}} |  Email: \underline{\href{mailto:rahul.nath.eph@gmail.com}{\color{blue}rahul.nath.eph@gmail.com}}\\
Cell: 516.491.9232 | Github: \underline{\href{https://github.com/rahul-nath}{\color{blue}rahul-nath}}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.31\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionsep

\subsection{Georgia Tech}
\descript{M.S. in Computer Science}
\location{August 2016 | \color{blue}\underline{\color{blue}\href{http://www.omscs.gatech.edu}{\color{blue}OMSCS}}}
{\footnotesize \textit{\textbf{Specialization in Machine Learning}}}}
{\footnotesize \textit{\textbf{(Incomplete)}}}}
\sectionsep

\subsection{Williams College}
\descript{B.S. in Computer Science \\ B.A. in Economics}
\location{June 2015 | Williamstown, MA}
{\footnotesize \textit{\textbf{Dean's List}}}, {\footnotesize \textit{\textbf{Class of 1960 Economics Scholar}}}
\sectionsep

\subsection{Glen Cove HS, Valedictorian}
\location{June 2011 |  Glen Cove, New York}
\sectionsep

\subsection{Relevant Coursework}
Database Systems Concepts \& Design \\
Information Security \\
Data Structures \& Algorithms {\footnotesize \textit{\textbf{(Also T.A.'d) }}} \\
Data Visualization and Analysis \\
Machine Learning for Trading \\
Human Computer Interaction \\


\\[1\baselineskip]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Technical}
\\[1\baselineskip]

\location{Primary Languages}
Python \textbullet{} Javascript (ES6+) \\
\\[1\baselineskip]

\location{Query Languages}
SQL \textbullet{} InfluxQL \textbullet{} Google DataStore \\
\\[1\baselineskip]

\location{Back-End}
Flask \textbullet{} SQLAlchemy (ORM) \textbullet{} InfluxDB \\
Pytest \textbullet{} NodeJS \textbullet{} SequelizeJS (ORM)   \\
Koa \textbullet{} PassportJS \textbullet{} PostgreSQL\\
Server-Side Rendering (Jinja)
\\[1\baselineskip]

\location{Infrastructure Exposure}
TCP/IP \textbullet{} Docker \textbullet{} NGINX \\
Kubernetes \textbullet{} Virtualbox/Vagrant \\
Redis \textbullet{} Unix/Linux \textbullet{} GCP \\
AWS EC2, S3 \textbullet{} Elasticsearch \\
\\[1\baselineskip]

\location{Front-End}
React \textbullet{} Redux \textbullet{} React Native \\
 HTML/CSS \textbullet{} Sagas \textbullet{} Jest/Enzyme \\
 BeautifulSoup \textbullet{} D3.js \\
\\[1\baselineskip]

% \location{Misc. Tools}
% JIRA/Confluence \textbullet{} Clubhouse \\
% Kibana \textbullet{} Chartio \textbullet{} Git/SVN \textbullet{} Asana \\
% \\[1\baselineskip]

% \location{Tools}
%  Slack API \textbullet{} Twilio API \textbullet{} YouTube API
%  Pandora Bots API \textbullet{} Chartio
%  Optimizely A/B \textbullet{} \textbullet{} Pandas
%  Numpy \textbullet{} Sklearn
\\[1\baselineskip]

\subsection{Spoken Languages}
\\[1\baselineskip]
Bengali (Intermediate Proficiency)
Spanish (Intermediate Proficiency) \\
French (Beginner Proficiency)\\

\section{Open-Source}
\textbullet{} \color{blue}\underline{\color{blue}\href{https://github.com/google/election_results_xml_validator}{\color{blue}Election XML Validator}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\sectionsep

\runsubsection{Google}
\descript{(via Scopus IT) | Solutions Engineer | \location{ 06/19 - Now }}
\vspace{\topsep}
\begin{tightemize}

\item Scale and deploy voter registration and live election results products.
\item Develop features for XML feed validator (Python).

\end{tightemize}
\sectionsep

\runsubsection{Pillar Technologies}
\descript{| Software Engineer | \location{ 05/18 - 05/19 }}
\vspace{\topsep}
\begin{tightemize}

\item Owned development of a supply-chain management system to manage IoT device deployments, shipments, and physical locations.
\item Worked on React Native onsite inventory management scanning app.
\item Generated time-series queries (InfluxDB), data viz (D3.js), \& Redis workers for onsite resource uptime data (GBs of data collected weekly).
\item Discovered API optimizations that reduced fetches by 50\%.

\end{tightemize}
\sectionsep


\runsubsection{WorkRails}
\descript{| Software Engineer | \location{07/17 - 12/17} }
\begin{tightemize}


% \item I work within the React/Redux frontend and NodeJS backend. I design and implement UX features, APIs, data models, \& DevOps.
% \item Developed partner custom login and SSO, calendar, work routing, and Developer API features, bringing in over \$20k in MRR.
% \item Decreased our production deployment time by 30\% by parallelizing pipelines of independent deployed clusters.

\item Second-hire engineer. Wrote APIs, data models, and UI features, end-to-end in React/Node microservices-based environment.
\item Owned development of custom company logins, SSO, calendar export, and contractor work assignment, bringing in over \$20k in MRR.

\end{tightemize}
\sectionsep

\runsubsection{Udacity}
\descript{| Course Manager/Software Dev | \location{08/15 - 07/16 }}
\begin{tightemize}

\item Owned development of a Python cron job that pulled, cleaned and stored YouTube metadata using AWS Redshift, then pipelined into Chartio for company-wide accessibility.
\item Re-invented the Intro to Programming Nanodegree into exploratory program to other courses, increasing enrollment by over 20\%.

\end{tightemize}
\sectionsep

\runsubsection{Naval Research Laboratory}
\descript{| A.I. Research Intern | \location{06/14 - 09/14 }}
\begin{tightemize}
\item Implemented a tool in Python that generates action models in polynomial time -- previously an intractable problem -- expanding the planning domain of environments for an A.I. agent to acquire knowledge.
\item Designed and implemented an algo to resolve prepositional ambiguity in interpreted speech using contextual info collected from sensor data.
\end{tightemize}
\sectionsep

\runsubsection{Other Technical Experience}
\descript{| Contract, Pro-Bono Developer}
\begin{tightemize}
\item Code Reviewer for Udacity Nanodegrees (07/16 - 07/17)
\item Scraped and performed analysis on donor info data to pass measures on universal healthcare as a volunteer developer for Fight For the Future.
\end{tightemize}

%\runsubsection{Mobiquity}
%\descript{| Android Developer Intern}
%\location{May 2014 – July 2014 | Wellesley, MA}
%\begin{tightemize}
%\item Helped implement health data collection for Mobiquity’s deltaIQ Android application. Used Amazon Kinesis, EC2 and Android (Java).
%\item Designed and implemented a prototype of an indoor navigation application using Node.js, iBeacons, Google Glass, and AWS (EC2, S3, Kinesis, and Cognito).
%\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}

\location{\color{blue}\underline{\href{https://github.com/rahul-nath/uDiary}{\color{blue}urDiary}}}
\begin{tightemize}
\item Developing an open-source Medium-like blog to help others record thoughts and experiences with the ability to dynamically organize their posts using special syntax. Leveraging React, Draft.js, Flask, and PostgreSQL
\end{tightemize}
\sectionsep

\location{\color{blue}\underline{\href{https://github.com/rahul-nath/PrePost2/blob/master/final_try.py}{\color{blue}PrePost2}}}
\begin{tightemize}
\item Using selenium, multiprocessing pools, and BeautifulSoup, I created a parallelized webscraper to collect documents and increase baseline accuracy of environment domain model generation by 25\%. These domain models are used by A.I. agents to plan its actions.
\end{tightemize}
\sectionsep

% \location{\underline{\color{blue}\href{https://github.com/rahul-nath/medicost}{\color{blue}Medicost}} (MIT Hack Medicine Team, 24-hr hackathon)}
% \begin{tightemize}
% \item Created a website to search for specialist doctors and procedure costs using public insurance claims data from the Department of HHS.
% \end{tightemize}


%\location{\color{blue}\underline{\href{https://github.com/ckan/ckan}{\color{blue}CKAN: Open-Source DMS }}}
%\begin{tightemize}
%\item I contribute to CKAN, the data hub that powers open data for governments.
%\end{tightemize}
%\sectionsep

\location{\color{blue}\underline{\href{https://github.com/rahul-nath/rentbot}{\color{blue}Rentbot}}}
\begin{tightemize}
\item Developed a chatbot designed to help SF residents learn their rights as tenants. Utilized Flask, Google App Engine, and Pandorabots API.
\end{tightemize}
\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}
