%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text
%\setlength\parindent{20pt}
%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
\newcommand{\forceindent}{\leavevmode{\parindent=24pt\indent}}
\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font
\pagenumbering{gobble}

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
% changed this
\textheight=9.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

%\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

%\begin{letter}{Mrs. Jane Smith \\
%Recruitment Officer \\
%The Corporation \\
%123 Pleasant Lane \\
%City, State 12345} 

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf Rahul Nath \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
Email: rahul.nath@williams.edu \\ Website: http://rahul-nath.github.io \\ Williams College \\ Williamstown, MA 01267
%11 Grove St. \\ Glen Cove, NY 11542 \\ (516)491-9232 % Your address and phone number
\end{center}

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------
\\ \\
Dear Recruiters at Trip Advisor,\\

\forceindent My greatest desire in life is to use coding and computer science to allow others experience the world and all its wonders. As a world traveler and coder, I find myself attracted to no other position in the world as much as a Software Engineering position at companies like Trip Advisor; the prospect of ambiguous or undefined challenges associated with it excites me. As a Computer Science and Economics double major at the one of the best liberal arts college in the country, I am constantly faced with handling ambiguous and undefined challenges. In confronting these challenges I have assembled an arsenal of tools that aid me in thinking creatively and abstractly. My talents in combating a variety of different technical challenges are no more evident than in my past internship and research experiences. \\

\forceindent I am a quick learner who expands and innovates on the knowledge I acquire. I especially love to learn about new technologies, which is why I spent this past summer developing applications using new technologies at Mobiquity Inc. I created an indoor location tracking Android application that logged user location using a combination of Amazon Kinesis and strategically located iBeacons. I also developed test apps that transmitted data to Amazon EC2 instances using secure OAuth authentication methods and aimed for scalability on the server side, giving me intimate knowledge of the MEAN stack. The projects I worked on have become products that Mobquity markets today under its $deltaIQ^{TM}$ behavioral change platform. \\ %I was also lucky to have direct guidance from the CTO, Android Platform Lead, and head of the Research and Development Lab.

\forceindent While my experiences at Mobiquity gave me hands-on design, business, and software engineering experience, I also had the opportunity to advance the state-of-the-art in knowledge engineering as an applied artificial intelligence researching contractor at the Naval Research Laboratory this summer, continuing into my fall semester at Williams as Senior Honors Research. Working under the Head of the Adaptive Systems Section on the Autonomous Squad Member Project (ASM), I used information retrieved from different sensors of the automaton to amortize the difficulty of increasing its knowledge about the world, all in Common Lisp. I also implemented a knowledge engineering algorithm in Python for comparison against a proprietary knowledge engineering algorithm for the purposes of automated planning and machine learning. \\

\forceindent My experiences in start-ups, mid-sized companies, and government research labs demonstrate the breadth of my knowledge in both academia and industry and make me the ideal candidate for a Software Engineering role at Trip Advisor. I appreciate your consideration for the position. \\ \\

Sincerely, \\ \\
Rahul Nath \\
William College Class of 2015  \\
Computer Science and Economics

%\encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

%\end{letter}

\end{document}
