\documentclass[]{deedy-resume-openfont}

\hypersetup{%
  colorlinks=true,% hyperlinks will be black
  urlcolor=blue
}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Rahul}{Nath}{ Website/Blog:\urlstyle{same} \underline{\href{http://therahulnath.com}{\color{blue} http://therahulnath.com}} |  Email: \underline{\href{mailto:rahul.nath.eph@gmail.com}{\color{blue}rahul.nath.eph@gmail.com}}\\
Cell: 516.491.9232 | Github: \underline{\href{https://github.com/rahul-nath}{\color{blue}rahul-nath}}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.31\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\sectionsep
\subsection{Georgia Tech}
\descript{M.S. in Computer Science}
\location{August 2016 | \color{blue}\underline{\color{blue}\href{http://www.omscs.gatech.edu}{\color{blue}OMSCS}}}
{\footnotesize \textit{\textbf{(Incomplete)}}}}\\
{\footnotesize \textit{\textbf{Specialization in Machine Learning}}}}
\sectionsep

\subsection{Williams College}
\descript{B.S. in Computer Science \\ B.A. in Economics}
\location{June 2015 | Williamstown, MA}
{\footnotesize \textit{\textbf{Dean's List}}}, {\footnotesize \textit{\textbf{Class of 1960 Economics Scholar}}}
\sectionsep

\subsection{Glen Cove HS, Valedictorian}
\location{June 2011 |  Glen Cove, New York}
\sectionsep

\subsection{Select Coursework}
Database Systems Concepts \& Design \\
Information Security \\
Data Structures \& Algorithms {\footnotesize \textit{\textbf{(Also T.A.'d) }}} \\
Data Visualization and Analysis \\
Machine Learning for Trading \\
Human Computer Interaction \\
\sectionsep


\section{Open-Source}
\color{blue}\underline{\color{blue}\href{https://github.com/google/election_results_xml_validator}{NIST Validator}} \\
\color{blue}\underline{\color{blue}\href{https://github.com/opencivicdata/ocd-division-ids}{Open Civic Data}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\sectionsep

\location{Primary Languages}
Python \textbullet{} Javascript \\
\\[1\baselineskip]

\location{Query Languages}
SQL \textbullet{} InfluxQL \textbullet{} Google DataStore \\
\\[1\baselineskip]

\location{Back-End}
Flask \textbullet{} SQLAlchemy \textbullet{} InfluxDB \\
MongoDB \textbullet{} PyMongo \textbullet{} NoSQL \\
Pytest \textbullet{} NodeJS \textbullet{} SequelizeJS  \\
Koa \textbullet{} PassportJS \textbullet{} PostgreSQL\\
\\[1\baselineskip]

\location{Infrastructure Exposure}
Docker \textbullet{} NGINX \textbullet{} AWS EC2, S3 \\
Kubernetes \textbullet{} Virtualbox/Vagrant \\
Unix/Linux \textbullet{} GCP \textbullet{} Redis\\
\\[1\baselineskip]

\location{Front-End}
React \textbullet{} Redux \textbullet{} React Native \\
 HTML/CSS \textbullet{} Sagas \textbullet{} Jest/Enzyme \\
 BeautifulSoup \textbullet{} D3.js \\
 Ant Design \textbullet{} Material UI \\
\\[1\baselineskip]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\sectionsep

\runsubsection{Google}
\descript{via Scopus IT | Solutions Engineer | \location{ 06/19 - 01/20 }}
\vspace{\topsep}
\begin{tightemize}

\item Developed Python/bash scripts to generate Search result config files.
\item Coded XML feed validator rules for NIST election formatted data.
\item Brought unit test coverage from 0 to 99\% (PyTest).

\end{tightemize}
\sectionsep

\runsubsection{Pillar Technologies}
\descript{| Software Engineer | \location{ 05/18 - 05/19 }}
\begin{tightemize}

\item Owned development of a supply-chain management system to manage IoT device inventory \& shipments (PostgreSQL, Flask, Docker, React).
%\item Worked on React Native onsite inventory management scanning app.
\item Generated time-series queries (InfluxDB), data visualizations (Ant Design, D3.js), \& Redis workers for GBs of onsite device uptime data.
\item Optimized API to reduce DB fetches by 50\% (SQLAlchemy).

\end{tightemize}
\sectionsep


\runsubsection{WorkRails}
\descript{| Software Engineer | \location{07/17 - 12/17} }
\begin{tightemize}

\item Second-hire engineer. Wrote APIs \& data models (SequelizeJS), UI features (React) and Node.js microservices (NGINX, Koa, Ingress).
\item Owned development of auth system (PassportJS), SSO, calendar export, and contractor work assignment, bringing in over \$20k in MRR.
\item Cut codebase in half over time. Took a 10k line file to 4500 in 1st week.

\end{tightemize}
\sectionsep

\runsubsection{Udacity}
\descript{| Course Manager/Software Dev | \location{08/15 - 07/16 }}
\begin{tightemize}

\item Developed ETL for YouTube data using Python to pull and clean, AWS Redshift to store, and Chartio to access company-wide.
% \item Owned development of a Python cron job that pulled, cleaned and stored YouTube metadata using AWS Redshift, then pipelined into Chartio for company-wide accessibility.
\item Re-invented the Intro to Programming Nanodegree into exploratory program to other courses, increasing enrollment by over 20\%.

\end{tightemize}
\sectionsep

\runsubsection{Naval Research Laboratory}
\descript{| A.I. Research Intern | \location{06/14 - 09/14 }}
\begin{tightemize}
\item Wrote scripts that generate action models for A.I. agents to improve knowledge and planning domain from intractable to polynomial time.
\item Designed and implemented an algo to resolve prepositional ambiguity in interpreted speech using contextual info collected from sensor data.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}

\location{Buddha Health}
\begin{tightemize}
\item A pill management app for my father. Locally deployed, it helps him and his doctors track frequent med and vital changes. Uses React, MongoDB \& Flask.
\end{tightemize}
\sectionsep

\location{\color{blue}\underline{\href{https://github.com/rahul-nath/uDiary}{\color{blue}urDiary}}}
\begin{tightemize}
\item An open-sourced, dynamically categorizing online reflection journal. Uses React, Material UI, Draft.js, Flask, and PostgreSQL. Hosted on Heroku and Zeit.
\end{tightemize}
\sectionsep

\location{\color{blue}\underline{\href{https://github.com/rahul-nath/PrePost2/blob/master/final_try.py}{\color{blue}PrePost2}}}
\begin{tightemize}
\item Using selenium, multiprocessing pools, and BeautifulSoup, I created a parallelized webscraper to collect documents and increase baseline accuracy of environment domain model generation by 25\%. These domain models are used by A.I. agents to plan its actions.
\end{tightemize}
\sectionsep

\location{\color{blue}\underline{\href{https://github.com/rahul-nath/rentbot}{\color{blue}Rentbot}}}
\begin{tightemize}
\item Developed a chatbot designed to help SF residents learn their rights as tenants. Utilized Flask, Google App Engine, and Pandorabots API.
\end{tightemize}
\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}
