\documentclass[]{deedy-resume-openfont}

% \hypersetup{%
%   colorlinks=true,% hyperlinks will be black
%   urlcolor=blue
% }

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Rahul}{Nath}{ Website/Blog:\urlstyle{same} \underline{\href{http://therahulnath.com}{\color{blue} http://therahulnath.com}} |  Email: \underline{\href{mailto:rahul.nath.eph@gmail.com}{\color{blue}rahul.nath.eph@gmail.com}}\\
Cell: 516.491.9232 | Github: \underline{\href{https://github.com/rahul-nath}{\color{blue}rahul-nath}}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.31\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\\[1\baselineskip]
\subsection{Georgia Tech}
\descript{M.S. in Computer Science}
\location{Candidate, Part-Time | \color{blue}\underline{\href{http://www.nytimes.com/2016/09/29/upshot/an-online-education-breakthrough-a-masters-degree-for-a-mere-7000.html}{\color{blue}OMSCS}}}
{\footnotesize \textit{\textbf{Specialization in Machine Learning}}}
\sectionsep

\subsection{Williams College}
\descript{B.S. in Computer Science \\ B.A. in Economics}
\location{June 2015 | Williamstown, MA}
{\footnotesize \textit{\textbf{Dean's List}}}, {\footnotesize \textit{\textbf{Class of 1960 Economics Scholar}}}
\sectionsep

\subsection{\underline{\href{https://patch.com/new-york/glencove/meet-glen-coves-valedictorian-rahul-nath}{\color{blue}GCHS, Valedictorian}}}
\location{June 2011 |  Glen Cove, New York}
\sectionsep

\subsection{Relevant Coursework}
Machine Learning for Trading \\
Hadoop and MapReduce (Udacity) \\
Data Visualization and Analysis \\
Data Structures \& Algorithms {\footnotesize \textit{\textbf{(Also T.A.'d) }}} \\
Information Security \\

\\[1\baselineskip]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\\[1\baselineskip]

\location{Primary Languages (1000+ lines):}
Python \textbullet{} Javascript
\\[1\baselineskip]

\location{Experience with:}
 Java \textbullet{} x86 Assembly \textbullet{} C
\\[1\baselineskip]

\location{Data Skills}
SQL \textbullet{} Pandas \textbullet{} NumPy \\
R \textbullet{} scikit-learn \textbullet{} BeautifulSoup \\
Hadoop/MapReduce (CDH, Cloudera) \\
ReactJS/Redux/D3.js \textbullet{} PostgreSQL \\
\\[1\baselineskip]

\location{Back-End:}
NodeJS \textbullet{} SequelizeJS \textbullet{} Koa\\
Flask \textbullet{} SQLAlchemy \textbullet{} PassportJS\\
Nginx \textbullet{} GCP DataStore\\
\\[1\baselineskip]

\location{Dev-Ops:}
Docker \textbullet{} Kubernetes \textbullet{} Apache \\
Wercker \textbullet{}  Quay \textbullet{} Vagrant \\
AWS EC2, S3, Redshift
\\[1\baselineskip]



\sectionsep

% \location{APIs and Tools}
%  Slack API \textbullet{} Twilio API \textbullet{} YouTube API
%  Pandora Bots API \textbullet{}  Vagrant \textbullet{} Chartio
%  Optimizely A/B \textbullet{} Docker \textbullet{} Pandas
%  Numpy \textbullet{} Sklearn

\subsection{Spoken Languages}
\\[1\baselineskip]
Spanish (Intermediate Proficiency) \\
French (Beginner Proficiency)\\
Bengali (Intermediate Proficiency)

% \section{Open-Source}
% \textbullet{} \color{blue}\underline{\color{blue}\href{}{\color{blue}CKAN: Open Source DMS}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{WorkRails Inc.}
\descript{| Software Engineer }
\location{July 2017 – Present | New York, NY}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}

\item I work within the React/Redux frontend and NodeJS backend. I design and implement UX features, APIs, data models, \& DevOps.
\item Developed partner custom login and SSO, calendar, work routing, and Developer API features, bringing in over \$20k in MRR.
\item Decreased our production deployment time by 30\% by parallelizing pipelines of independent deployed clusters.

\end{tightemize}
\sectionsep

\runsubsection{Udacity}
\descript{| Course Manager/Software Dev}
\location{Aug 2015 – July 2016 | Mountain View, CA}
\begin{tightemize}

\item Re-invented Intro to Programming Nanodegree (IPND) into exploratory program to other courses, increasing its enrollment by over 20\%.

%\item Created webcast teaching sessions and authored lessons on virtualization and Python optimization constructs.
%\item Created content and QA'd for Machine Learning, DevOps \& Android Basics.

% \item I conceptualized and developed Udacity's first student-to-student Q\&A video platform -- a full-stack project dubbed T.A. Sessions with integrated Slack orientation bot for over 2000 students. Leveraged Google App Engine, DataStore, and Ruby on Rails.
\item Automated student YouTube data collection for all Nanodegree webcasts. I wrote a Python cron job that pulled, formatted and stored the data using AWS Redshift. Data then pipelined into Chartio for company-wide accessibility.
\end{tightemize}
\sectionsep

\runsubsection{Naval Research Laboratory}
\descript{| Contractor }
\location{July 2014 – Sept 2014 | National Harbor, MD}
\begin{tightemize}
\item Implemented a tool in Python that generates action models in polynomial time -- previously an intractable problem -- expanding the planning domain of environments for an A.I. agent to acquire knowledge.

\item Designed and implemented an algorithm in Lisp and Python to resolve prepositional and word-sense ambiguity in natural language processing using collected contextual information.
\end{tightemize}
\sectionsep

\runsubsection{Mobiquity}
\descript{| Android Developer Intern}
\location{May 2014 – July 2014 | Wellesley, MA}
\begin{tightemize}
\item Helped implement health data collection for Mobiquity’s deltaIQ Android application. Used Amazon Kinesis EC2 and Android (Java).

\item Designed and implemented a prototype of an indoor navigation application using Node.js, iBeacons, Google Glass, and AWS (EC2, S3, Kinesis, and Cognito).
\end{tightemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}

\location{\color{blue}\underline{\href{https://github.com/rahul-nath/PrePost2/blob/master/final_try.py}{\color{blue}PrePost2}}}
\begin{tightemize}
\item Using selenium, multiprocessing pools, and BeautifulSoup, I created a webscraper to collect documents and increase the accuracy of environment domain models by 25\%. Domain models are used by A.I. agents to plan actions.
\end{tightemize}

\location{\color{blue}\underline{\href{https://github.com/rahul-nath/trading_algos}{\color{blue}Trading Algorithms}}}
\begin{tightemize}
\item A repository of machine learning tools I wrote for graduate school and have extended to aid in exploring alpha in the stock market. (Pandas, NumPy, Deep Learning)
\end{tightemize}

\location{\color{blue}\underline{\href{https://github.com/rahul-nath/predicting_housing_prices/blob/master/boston_housing.ipynb}{\color{blue}"Predicting Boston Housing Prices" (Udacity)}}}
\begin{tightemize}
\item I evaluated the performance and predictive power of a model that has been trained and tested on data collected from homes in Boston suburbs.
\end{tightemize}


\location{\color{blue}\underline{\href{https://rahul-nath.github.io/docs/youth_programs_paper.pdf}{\color{blue}"From Play to Work: Effect of Youth Programs on Dropout Rates" (Term Paper)}}}
\begin{tightemize}
% \item An econometric study I performed exploring the relationship between high school drop out rates and extracurricular programs. Analysis available.
\item I used dprobit regression to explore the effect of extracurricular program attendance on the likelihood of dropping out of high school for at-risk students.
\end{tightemize}

% \location{\color{blue}\underline{\href{https://github.com/ckan/ckan}{\color{blue}CKAN: Open-Source DMS }}}
% \begin{tightemize}
% \item I contribute to CKAN, the data hub that powers open data for governments. 
% \end{tightemize}

\location{\underline{\color{blue}\href{https://github.com/rahul-nath/medicost}{\color{blue}Medicost}} (MIT Hack Medicine Team, 24-hr hackathon)}
\begin{tightemize}
\item Created a website to search for specialist doctors and procedure costs using public insurance claims data from the Department of HHS. (Pandas, Flask)
\end{tightemize}
% \sectionsep


\end{minipage}
\end{document}  \documentclass[]{article}
