\documentclass[]{deedy-resume-openfont}

% \hypersetup{%
%   colorlinks=true,% hyperlinks will be black
%   urlcolor=blue
% }

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Rahul}{Nath}{ Website/Blog:\urlstyle{same} \underline{\href{http://therahulnath.com}{\color{blue} http://therahulnath.com}} |  Email: \underline{\href{mailto:rahul.nath.eph@gmail.com}{\color{blue}rahul.nath.eph@gmail.com}}\\
Cell: 516.491.9232 | Github: \underline{\href{https://github.com/rahul-nath}{\color{blue}rahul-nath}}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.31\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\\[1\baselineskip]

\subsection{Williams College}
\descript{B.S. in Computer Science \\ B.A. in Economics}
\location{June 2015 | Williamstown, MA}
{\footnotesize \textit{\textbf{Dean's List}}}, {\footnotesize \textit{\textbf{Class of 1960 Economics Scholar}}}
\sectionsep

\subsection{\underline{\href{https://patch.com/new-york/glencove/meet-glen-coves-valedictorian-rahul-nath}{\color{blue}GCHS, Valedictorian}}}
\location{June 2011 |  Glen Cove, New York}
\sectionsep

\subsection{Relevant Coursework}
Machine Learning for Trading \\
Data Visualization and Analysis \\
Data Structures \& Algorithms {\footnotesize \textit{\textbf{(Also T.A.'d) }}} \\
Human Computer Interaction \\
Information Security \\

\\[1\baselineskip]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\\[1\baselineskip]

\location{Primary Languages (1000+ lines):}
Python \textbullet{} Javascript \textbullet{}  SQL
\\[1\baselineskip]

\location{Familiarity with:}
 C \textbullet{} x86 Assembly \textbullet{} Java
\\[1\baselineskip]

\location{Front-End Experience:}
ReactJS \textbullet{} Redux \textbullet{} webpack \\ 
React Native \textbullet{} Jinja2 \textbullet{} MaterialUI \\
React-Router \textbullet{} DraftJS \textbullet{}
BeautifulSoup \textbullet{} Bootstrap \\
\\[1\baselineskip]

\location{Back-End:}
NodeJS \textbullet{} SequelizeJS \textbullet{} Koa\\
PassportJS \textbullet{} PostgreSQL \textbullet{} Nginx \\
Flask \textbullet{} Django \textbullet{} SQLAlchemy \\
GAE \textbullet{} Firebase \\
\\[1\baselineskip]

% {\footnotesize \textit{\textbf{Experience with }}} \\


\location{Dev-Ops:}
Docker \textbullet{} Kubernetes \textbullet{} Apache \\
Wercker \textbullet{} Vagrant \textbullet{} AWS \\
\\[1\baselineskip]

\location{Other Skills}
Git/SVN \textbullet{} Linux \\
\\[1\baselineskip]

\sectionsep

% \location{APIs and Tools}
%  Slack API \textbullet{} Twilio API \textbullet{} YouTube API
%  Pandora Bots API \textbullet{}  Vagrant \textbullet{} Chartio
%  Optimizely A/B \textbullet{} Docker \textbullet{} Pandas
%  Numpy \textbullet{} Sklearn

\subsection{Spoken Languages}
\\[1\baselineskip]
Spanish (Intermediate Proficiency) \\
French (Beginner Proficiency)\\
Bengali (Intermediate Proficiency)

% \section{Open-Source}
% \textbullet{} \color{blue}\underline{\color{blue}\href{}{\color{blue}CKAN: Open Source DMS}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Civic}
\descript{| Software Engineer }
\location{January 2017 - Present | Remote}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}

\item Volunteer Engineer on a team building a holistic platform for voter registration.
\item Leveraging React Native and Firebase.

\end{tightemize}
\sectionsep

\runsubsection{WorkRails}
\descript{| Software Engineer }
\location{July 2017 – December 2017 | New York, NY}
\begin{tightemize}

\item Full Stack Engineer for a venture-backed startup with clients.
\item Developed UI features using React/Redux and implemented APIs and data models with NodeJS and Sequelize ORM. Managed products end-to-end.
\item Features created include custom login, SSO, calendar export, work routing, and Developer API features, bringing in over \$20k in MRR.
% \item Decreased our production deployment time by 30\% by suggesting we parallelize the deployment of independent pod clusters.

\end{tightemize}
\sectionsep

\runsubsection{Misc. Technical Roles}
\location{July 2016 – July 2017 | New York, NY}
\begin{tightemize}

\item Code Reviewer for Udacity courses (contract work)
\item Developed a \color{blue}\underline{\href{https://github.com/rahul-nath/rentbot}{\color{blue}chatbot}} to help SF tenants learn their rights as volunteer developer for Generation Citizen.
\item Scraped and performed analysis on donor info data to pass measures on universal healthcare in NY as a volunteer developer for Fight For the Future
\end{tightemize}
\sectionsep


\runsubsection{Udacity}
\descript{| Course Manager/Software Dev}
\location{Aug 2015 – July 2016 | Mountain View, CA}
\begin{tightemize}

\item Re-invented Intro to Programming Nanodegree (IPND) into exploratory program to other courses, increasing its enrollment by over 20\%.

%\item Created webcast teaching sessions and authored lessons on virtualization and Python optimization constructs.
%\item Created content and QA'd for Machine Learning, DevOps \& Android Basics.

% \item I conceptualized and developed Udacity's first student-to-student Q\&A video platform -- a full-stack project dubbed T.A. Sessions with integrated Slack orientation bot for over 2000 students. Leveraged Google App Engine, DataStore, and Ruby on Rails.
\item Automated student YouTube data collection for all Nanodegree webcasts. I wrote a scheduled Python script that pulled, cleaned, and stored video metadata. Data stored in Redshift, accessed through Chartio.
\end{tightemize}
\sectionsep

\runsubsection{Naval Research Laboratory}
\descript{| Student Contractor }
\location{July 2014 – Sept 2014 | National Harbor, MD}
\begin{tightemize}
\item Implemented an algorithm that generates action models in polynomial time -- previously an intractable problem -- expanding the planning domain of environments for an A.I. agent to acquire knowledge.

\item Designed and implemented an algorithm in Lisp and Python to resolve prepositional ambiguity in interpreted speech using contextual information collected from sensor data.
\end{tightemize}
\sectionsep

% \runsubsection{Mobiquity}
% \descript{| Android Developer Intern}
% \location{May 2014 – July 2014 | Wellesley, MA}
% \begin{tightemize}
% \item Implemented health data collection for Mobiquity’s deltaIQ Android app to inform lifestyle changes.

% \item Designed and implemented an indoor navigation Android app prototype using iBeacons, Google Glass, and AWS. Collected streaming data with AWS Kinesis.
% \end{tightemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}

% \location{\color{blue}\underline{\href{https://github.com/ckan/ckan}{\color{blue}CKAN: Open-Source DMS }}}
% \begin{tightemize}
% \item I contribute to CKAN, the data hub that powers open data for governments.
% \end{tightemize}
% \sectionsep

\location{\color{blue}\underline{\href{https://github.com/rahul-nath/uDiary}{\color{blue}uDiary}}}
\begin{tightemize}
\item Developing an open-source Medium-like blog to help others record thoughts and experiences with the ability to dynamically organize their posts using special syntax. Leveraging ReactJS, Flask, PostgreSQL, and Draft.js 
\end{tightemize}
\sectionsep


\location{\color{blue}\underline{\href{https://github.com/rahul-nath/PrePost2/blob/master/final_try.py}{\color{blue}PrePost2}}}
\begin{tightemize}
\item Using selenium, multiprocessing pools, and BeautifulSoup, I created a parallelized webscraper to collect documents and increase the accuracy of environment domain models by 25\%. These domain models are used by A.I. agents to plan its actions.
\end{tightemize}
\sectionsep

\location{\underline{\color{blue}\href{https://github.com/rahul-nath/medicost}{\color{blue}Medicost}} (MIT Hack Medicine Team, 24-hr hackathon)}
\begin{tightemize}
\item Created a website to search for specialist doctors and procedure costs using public insurance claims data from the Dept of Health \& Human Services.
\end{tightemize}

\end{minipage}
\end{document}  \documentclass[]{article}
