%----------------------------------------------------------------------------------------
%    PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text
%\setlength\parindent{20pt}
%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
\newcommand{\forceindent}{\leavevmode{\parindent=24pt\indent}}
\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font
\pagenumbering{gobble}

% Margins
\topmargin=-1.75in % Moves the top of the document 1 inch above the default
% changed this
\textheight=9.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

%\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{Mr. Jordan Weber \\
IMCA Capital \\
11620 Wilshire Blvd Ste. 600 \\
Santa Monica, CA 90025} 


%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf Rahul Nath \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
Email: rahul.nath@williams.edu \\ Williams College \\ Williamstown, MA 01267
%11 Grove St. \\ Glen Cove, NY 11542 \\ (516)491-9232 % Your address and phone number
\end{center}

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Mr. Weber,}

%\forceindent (Name of company) challenges the people of the world to learn more about each other through (medium of interest); correspondingly, the world challenges (Name of company) with ambiguous and often undefined tasks to facilitate this endeavor. 
\forceindent My Williams education, work experiences, and extracurricular activities have prepared me with the analytical tools to combat quantitative tasks of statistical and programmatic nature; I am well prepared for a career as an Account Executive in  Private Equity and Business Finance at IMCA Capital.

\forceindent Williams is a rigorous academic environment. It has equipped me with technical expertise in using statistical tools such as STATA, R, Python libraries, and Excel and developing economic models, both quantitative (multiple regression) and qualitative (strategic). I have written technical papers both independently and with teams on everything from exploring infant mortality rates in third world countries to case studies on the San Miguel Corporation to machine learning, and presented them to classmates, professors, and senior consultants alike. Intercollegiate debate and even my tenure as president of my mock trial team in high school has supplemented my classroom work in honing my public speaking, market/law research, and teamwork coordination skills. My academic training has shaped me into a scrupulous yet opportunistic decision maker in a multitude of different environments.

% prepared in business setting
%% introduced to executive structure and how a business runs at Mobiquity and MIL
%%% and even how government executive structure runs
%% learned about finding markets for products and actually utilizing competitive advantage
%% actually researched the latest in wearable technologies and state-of-the-art in SR engines
%% running due diligence on potential products in the mobile app market
%% gained practice in teamwork coordination in a software development setting

\forceindent The past few summers I have chosen opportunities that have allowed me to nurture my business and technical acumen alike. At  Middlebury Interactive Languages my sophomore year, I observed how a business runs from the top-down while also identifying deficiences and suggesting improvements with regards to the company's main product line; I reported directly to the COO. At Mobiquity, I worked closely with the CTO, Android Platform Lead, and R\& D Director, learning how to pitch, develop, and market mobile application products. Actually developing products allowed me to understand factors of sustainable growth for companies offering technical services. I also learned about the latest developments in mobile applications such as in wearable technology, eventually giving a presentation on the subject at AnDevCon 2014 in Boston. 

%After becoming well versed in these products, I gave a presentation on Google Glass and iBeacons at  conference. Moreover, I earned Amazon Web Services' Business Professional Accreditation, certifying the knowledge I have gained in the lastest cloud computing services offered by AWS, including Kinesis and Cognito. 

\forceindent My academic training and business experiences in start-ups and mid-sized companies demonstrate the breadth of my knowledge in both academia and industry and make me the ideal candidate for a Account Executive in  Private Equity and Business Finance position at IMCA Capital. I appreciate your consideration for the role. \\ 

Sincerely,\\ \\
Rahul Nath \\
William College Class of 2015  \\
Computer Science and Economics \\


%\encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}
