\documentclass[]{deedy-resume-openfont}

% \hypersetup{%
%   colorlinks=true,% hyperlinks will be black
%   urlcolor=blue
% }

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Rahul}{Nath}{ Website/Blog:\urlstyle{same} \underline{\href{http://therahulnath.com}{\color{blue} http://therahulnath.com}} |  Email: \underline{\href{mailto:rahul.nath.eph@gmail.com}{\color{blue}rahul.nath.eph@gmail.com}}\\
Cell: 516.491.9232 | Github: \underline{\href{https://github.com/rahul-nath}{\color{blue}rahul-nath}}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.31\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\\[1\baselineskip]
\subsection{Georgia Tech}
\descript{M.S. in Computer Science}
\location{Candidate, Part-Time | \color{blue}\underline{\href{http://www.nytimes.com/2016/09/29/upshot/an-online-education-breakthrough-a-masters-degree-for-a-mere-7000.html}{\color{blue}OMSCS}}}
{\footnotesize \textit{\textbf{Specialization in Machine Learning}}} 
\sectionsep

\subsection{Williams College}
\descript{B.S. in Computer Science \\ B.A. in Economics}
\location{June 2015 | Williamstown, MA}
{\footnotesize \textit{\textbf{Dean's List}}}, {\footnotesize \textit{\textbf{Class of 1960 Economics Scholar}}}
\sectionsep

\subsection{\underline{\href{https://patch.com/new-york/glencove/meet-glen-coves-valedictorian-rahul-nath}{\color{blue}GCHS, Valedictorian}}}
\location{June 2011 |  Glen Cove, New York}
\sectionsep

\subsection{Relevant Coursework}
High Performance Parallel Algorithms \\
Intro To Information Security \\
Machine Learning for Trading \\
Data Structures \& Algorithms {\footnotesize \textit{\textbf{(Also T.A.'d) }}} \\
Operating Systems
\\[1\baselineskip]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\\[1\baselineskip]

\location{Primary Languages (1000+ lines):}
Python \textbullet{}     C     \textbullet{} Java  
\\[1\baselineskip]

\location{Familiarity with:}
SQL \textbullet{} Javascript \textbullet{} x86 Assembly
\\[1\baselineskip]

\location{Experience with:}
Flask \textbullet{} SQLAlchemy ORM \\
\textbullet{} BeautifulSoup \textbullet{} Unix/Linux \\ 
Git/SVN \textbullet{} Google App Engine \\
\\[1\baselineskip]
Jinja2  \textbullet{} AWS EC2 \textbullet{} PostgreSQL \\
AWS Redshift \textbullet{} Apache \textbullet{} Nginx\\ 
Solr \textbullet{} Jetty \textbullet{} Bootstrap \textbullet{} IPSec
\sectionsep

\location{APIs and Tools}
  Slack API \textbullet{} Twilio API \textbullet{} YouTube API 
  Pandora Bots API \textbullet{}  Vagrant \textbullet{} Chartio 
  Optimizely A/B \textbullet{} Docker \textbullet{} Pandas 
  Numpy \textbullet{} Sklearn
\sectionsep
\\[1\baselineskip]

\subsection{Spoken Languages}
\\[1\baselineskip]
Spanish (Intermediate Proficiency) \\
French (Beginner Proficiency)\\
Bengali (Intermediate Proficiency)

% \section{Open-Source}
% \textbullet{} \color{blue}\underline{\color{blue}\href{}{\color{blue}CKAN: Open Source DMS}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Udacity}
\descript{| Course Manager}
\location{Aug 2015 – July 2016 | Mountain View, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}

\item Re-invented Intro to Programming Nanodegree (IPND) into exploratory program to other courses, increasing its enrollment by over 20\% -- the fastest growing nanodegree at Udacity.

\item Created webcast teaching sessions and authored lessons on virtualization and Python optimization constructs.

\item Created content and QA'd for Machine Learning, DevOps \& Android Basics.
\end{tightemize}

\vspace{\topsep} % Hacky fix for awkward extra vertical space

\runsubsection{Udacity }
\descript{| as Software Developer}
\location{}
\begin{tightemize}

\item I conceptualized and developed Udacity's first student-to-student Q\&A video platform -- a full-stack project dubbed T.A. Sessions with integrated Slack orientation bot for over 2000 students. Leveraged Google App Engine, DataStore, and Ruby on Rails.

\item Automated student YouTube data collection for Udacity webcasts. I wrote a Python cron job that collected over 8 million data points, formatted and stored the data on Udacity's AWS RedShift server, and pipelined it into Chartio.

\end{tightemize}
\sectionsep

\runsubsection{Naval Research Laboratory}
\descript{| Contractor }
\location{July 2014 – Sept 2014 | National Harbor, MD}
\begin{tightemize}
\item Implemented a tool in Python for A.I. robot to learn actions in polynomial time -- a previously intractable problem -- making it feasible to automate the process of environment knowledge acquisition.

\item Designed and implemented an algorithm in Lisp and Python to reduce prepositional and word-sense ambiguity in interpreted speech using contextual information.
\end{tightemize}
\sectionsep

\runsubsection{Mobiquity}
\descript{| Android Developer Intern}
\location{May 2014 – July 2014 | Wellesley, MA}
\begin{tightemize}
\item Implemented communication and data collection between an EC2 server and an Android application for Mobiquity’s deltaIQ platform.

\item Created the UX, UI, and business logic for an indoor navigation application using Node.js, iBeacons, Google Glass, and AWS EC2, S3, Kinesis, and Cognito.
\end{tightemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}

\location{\color{blue}\underline{\href{https://github.com/ckan/ckan}{\color{blue}CKAN: Open-Source DMS }}}
\begin{tightemize}
\item I contribute to CKAN, the data hub that powers open data for governments around the world. CKAN instances use Apache, Nginx, Jetty and Python.
\end{tightemize}
\sectionsep

\location{\color{blue}\underline{\href{https://github.com/rahul-nath/rentbot}{\color{blue}Rentbot}}}
\begin{tightemize}
\item Helped create a chatbot designed to help San Francisco residents learn their rights as renters. Utilized Flask, Google App Engine, and Pandorabots API.
\end{tightemize}
\sectionsep

\location{\color{blue}\underline{\href{https://github.com/rahul-nath/PrePost2/blob/master/final_try.py}{\color{blue}PrePost2}}}
\begin{tightemize}
\item Using selenium, multiprocessing pools, and BeautifulSoup, I created a webscraper to collect documents and suggest 25\% more accurate environment domain models to be used by an artificially intelligent agent planning its actions. 
\end{tightemize}
\sectionsep

\location{\underline{\color{blue}\href{https://github.com/rahul-nath/medicost}{\color{blue}Medicost}} (MIT Hack Medicine Team, 24-hr hackathon)}
\begin{tightemize}
\item Created a website to easily search cost requests and receipts made by doctors, standardizing expensive medical procedure costs for over 44 million Americans without medical insurance. We used Flask, Grunt, JQuery, and Bootstrap.
\end{tightemize}

\end{minipage} 
\end{document}  \documentclass[]{article}
