%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{Flatiron Health \\
200 Fifth Avenue, 8th Fl \\
New York, NY 10010} 

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf Rahul Nath \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
2135 Finch Lane \\ Central Islip, NY 11722 \\ (516) 491-9232 % Your address and phone number
\end{center}

\signature{Rahul Nath} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Recruiters,} 
 
I am writing to express my formal interest in applying for a role as a backend software engineer at Flatiron Health. After learning more about the company from a current engineer and former classmate, Matt McNaughton, I immediately thought that this would be the perfect role, and Flatiron Health the perfect company, for me. 
\\

Advancing research and early detection of cancer is critical to stopping it in its tracks. My grandmother and uncle in the U.S. owe their lives to early detection of breast and prostate cancers, and my grandfather suffered his death to cancer for a lack thereof in Calcutta. I've felt enough anxiety over this terrible condition to not do something about it now. 

Over my career so far, I have amassed experience in backend engineering and data engineering, including implementation of several internal tools I developed at Udacity. I have also had experience developing healthcare-related applications. In an internship as an Android Developer at Mobiquity Inc., I developed a health data collection application and at MIT's Hack Medicine Hackathon, I created a web app called Medicost that provides easy access to medical treatment cost information based on data pulled from the Department of HHS. Flatiron Health is truly the perfect amalgamation of my career interests. 
 \\

I would love to set up an initial phone call with a recruiter. I live in New York, and I am available most days for a conversation. I am best contacted through email, which is also on my resume: rahul.nath.eph@gmail.com. Thank you for your time and consideration.

\closing{Sincerely,}

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}