\documentclass[]{deedy-resume-openfont}

% \hypersetup{%
%   colorlinks=true,% hyperlinks will be black
%   urlcolor=blue
% }

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Indrani}{Nath}{ Address:\urlstyle{same} 2135 Finch Lane, Islip, NY 11722 \\
Cell: 516.330.6616 | Email: indrani.nath1957@gmail.com}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.31\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\\[1\baselineskip]
\section{Education} 
\\[1\baselineskip]

\subsection{Adelphi University}
\descript{B.S in Nursing (R.N.)}
\location{June 2006 | Garden City, NY}
\sectionsep

\subsection{Kiev State Medical Institute }
\descript{M.D., General Physician}
\location{June 1983 | Kiev, Ukraine}
\\[1\baselineskip]

\subsection{Medical Certifications}
\textbullet{} Recertified and Updated CPR (2017) \\
\sectionsep
\textbullet{} Case Management \\
Certification (2010) \\
\sectionsep
\textbullet{} NCLEX by State Board (2007) \\
\sectionsep
\textbullet{} C.N.A. Certificate (1998) \\
\sectionsep
\textbullet{} Certificate in \\
Echocardiography (1995) \\
\sectionsep
\textbullet{} Certificate in \\
Diagnostic Ultrasound (1994)
\\[1\baselineskip]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\\[1\baselineskip]

\subsection{Spoken Languages}
\\[1\baselineskip]
\textbullet{} Spanish (Beginner Proficiency) \\
\sectionsep
\textbullet{} Hindi (Advanced Proficiency) \\
\sectionsep
\textbullet{} English (Fluent) \\
\sectionsep
\textbullet{} Russian (Fluent) \\
\sectionsep
\textbullet{} Bengali (Fluent) \\
\\[1\baselineskip]

\subsection{Medical Expertise}
\\[1\baselineskip]

\textbullet{} Taking blood draws, finger sticks, \\
injections, and vitals \\ 
\sectionsep
\textbullet{} IV pump and central line maintenance \\ 
\sectionsep
\textbullet{} Excellent communication skills \\
\sectionsep
\textbullet{} Patient education on medication \\
\sectionsep
\textbullet{} HIPAA \& JCAHO Knowledge \\
\sectionsep
\textbullet{} Experience with G-tube feeding \\
\sectionsep
\textbullet{} Provision of trach and vent care \\
\\[1\baselineskip]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Substitute Nurse}
\descript{Long Island Public Schools}
\location{June 2009 – Present}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}

\item Worked at multiple schools across Nassau, Suffolk, Queens, and Brooklyn.

\item Responsible for checking vital signs of students between the ages of 5 and 18.

\item Cared for children with special needs like those with diabetes, intellectual disabilities, G-Tubes, and asthma

\item Would give hearing and vision tests and manage emergency situations

\end{tightemize}
\sectionsep

\runsubsection{Home Care R.N.}
\descript{Horizon Health Staffing}
\location{July 2007 – Present | Roslyn, NY}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}

\item One-to-one care of patients confined to bed. 

\item Responsibilities included bathing, grooming, maintain patient’s personal hygiene, administering medication, assisting in G-Tube feeding, maintaining the Foley catheter of the patient.

\end{tightemize}
\sectionsep


\runsubsection{Nursing Home Staff R.N.}
\descript{Staffing Remedies and Juno Healthcare}
\location{Nov 2005 - Oct 2012}
\begin{tightemize}

\item Responsible for up to 45 patients at a time, administering G-Tube feeding, insulin administration, finger sticks, and intramuscular injections -- lovenox, antibiotics, IV, Heparin, Piperacillin, and transdermal patches. 

\item Settings would be anywhere from 100 to 500 beds. Patients would range from diabetics to IV patients and those requiring sub-acute care. Attending teams would include 1 LPN and 1 RN.

\item Staffed at multiple nursing home facilities across Long Island, including Meadowbrook Care Center, Marquis Care Center, Avalon Care Center, and Long Island Care Center, and Hillside Manor Nursing Home.

\end{tightemize}
\sectionsep


\runsubsection{Hospital R.N.}
\descript{New York Presbyterian}
\location{June 2007 - July 2008}
\begin{tightemize}

% \item Hospitals included  in Sea Cliff, NY,  in Manhattan, NY, and  in Brooklyn, NY.

% \item Assessed and formulated of Oasis 485 Care Plan for patients

\item Facilitated admissions assessment, transfer, discharge, and education of patients and emergency patients, including educating and supervising home health aides and preparing chart notes

\item Cared for diabetic patients, chronic patients, and seizure patients

\item Would administer first-aid in emergency situations and preservation of photographic records of incidents.  

\item Assisted tracheostomy patients with trach and vent support, replaced internal cannulas, suctioned under pulse oxymeter, inserted and maintained catheters, handled medication administration, dressing changes, and IVs

\item Responded to numerous volatile situations and violent outbreaks, earning the respect of physicians and coworkers for calm, levelheaded and quick thinking to restore the safety and security of patients and staff.

\end{tightemize}
\sectionsep


\runsubsection{Licensed Practical Nurse}
\descript{Interpid USA Nursing Agency}
\location{June 2005 - Apr 2007}
\begin{tightemize}


\item Responsible for 30 – 35 patients on a given floor

\item Administered medication, narcotic counts, finger sticks, G-Tube feeding, and writing 24-Hour Nurse’s Notes.

\item Facilities included Meadowbrook Care Center in Freeport, NY; Long Care Center in Queens, NY; Dry Harbor Care Center in Queens; and Fulton Commons in Hempstead, NY

\end{tightemize}
\sectionsep

% \runsubsection{Certified Nursing Assistant}
% \descript{Glengariff Healthcare Center}
% \location{June 2000 - June 2003 | , Glen Cove, NY}
% \begin{tightemize}

% \item Actively cared for 10-12 patients on the floor including bathing, showering, and maintenance of physical fitness and hygiene

% \item Would help patients in using Hoyer system to transfer them from bed to wheelchair.
% \end{tightemize}


% Key Accomplishments:
% 

% 
% Treated an average of 40 patients daily as LPN and RN


\end{minipage} 
\end{document}  \documentclass[]{article}
